cardinalR: Generating interesting high-dimensional data structures

### 2025-08-21 paper-cardinalR.Rmd
Initial work on adding the multi cluster table

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_multigrid",
                                "make_threeclust01",
                                "make_fourclust01",
                                "make_fiveclust01"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

>>>>

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

### 2025-08-21 paper-cardinalR.tex
Initial work on adding the multi cluster table

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
make\_curvygau & \\
make\_multigrid & \\
make\_threeclust01 & \\
\addlinespace
make\_fourclust01 & \\
make\_fiveclust01 & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
make\_curvygau & \\
make\_klink\_circles & \\
make\_chain\_circles & \\
\addlinespace
make\_klink\_curvycycle & \\
make\_chain\_curvycycle & \\
make\_gaucircles & \\
make\_gaucurvycycle & \\
make\_onegrid & \\
\addlinespace
make\_twogrid\_overlap & \\
make\_twogrid\_shift & \\
make\_shape\_para & \\
make\_three\_clust\_ & \\
\bottomrule
\end{tabular}
\end{table}
